pirouette: Determining the error BEAST2 makes in inferring a phylogeny

### 2019-03-08 article.tex
Results of 6 percent of proteome

@@

>>>>

There are thousands of MHC2 alleles known.
For this research, we picked the three alleles that are most abundant,
accoring to \richel{reference here}, 
which are DRB4*0101, 
HLA-DPA10103-DPB10402 
\richel{
  we decided for DPB1*0402, but there are multiple alleles matching.
  I just picked the first one of the alleles matching, which are:
  HLA-DPA10103-DPB10402,
  HLA-DPA10104-DPB10402,
  HLA-DPA10105-DPB10402,
  HLA-DPA10106-DPB10402,
  HLA-DPA10107-DPB10402,
  HLA-DPA10108-DPB10402,
  HLA-DPA10109-DPB10402,
  HLA-DPA10110-DPB10402,
  HLA-DPA10201-DPB10402,
  HLA-DPA10202-DPB10402,
  HLA-DPA10203-DPB10402,
  HLA-DPA10204-DPB10402,
  HLA-DPA10301-DPB10402,
  HLA-DPA10302-DPB10402,
  HLA-DPA10303-DPB10402,
  HLA-DPA10401-DPB10402
}
and DQA1*0501/DQB1*0301,
that are present in respectively 31, 41 and 59 percent 
\richel{fix numbers}
of the current human population.

@@

\begin{table}
\centering
  \begin{tabular}{| r | c | c | c | c | c | c |}
    \hline
    \textbf{Allele}       & \textbf{i} & \textbf{m} & \textbf{o} & \textbf{I} & \textbf{M} & \textbf{O} \\ 
    \hline
    DRB4*0101             & 3752 & 2397 & 62024 & 1061 & 854  & 11952 \\
    HLA-DPA10103-DPB10402 & 4335 & 2328 & 69040 & 478  & 923  & 4936 \\
    DQA1*0501/DQB1*0301   & 3321 & 1329 & 45461 & 1492 & 1922 & 28515 \\
    \hline 
  \end{tabular}
  \caption{
    Results \richel{These are preliminary, 6 percent of proteome}
  }
  \label{tab:results}
\end{table}
